---
title: "Run_CSIA_full_run"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Run_CSIA_full_run}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



## Started: 07-07-2021: Nowakowski
## Updated: 08-09-2021: Nowakowski
## Updated: 03-16-2022: Nowakowski

## DO NOT CHANGE THE EXAMPLE_HOME.R FILE!! 
## PLEASE SAVE A NEW ONE WITH YOUR NAME OR PROJECT IN THE FILE NAME AND EDIT YOUR RUN SETTINGS FROM THERE

## SAVE THIS TO THE HOME FILE - THIS IS WHERE ALL FILES THAT MAY BE CHANGED LIVE. 

## NEVER EDIT A FILE IN THE SOURCE FOLDER WITH OUT SAVING A COPY SEPERATLY FIRST

## variables defined in this file are global and can be used by all functions


#################################################
## Current errors that run and code could be adjusted for
## Note: Current case that does not work is if one sample has meth and the other two do not AND the standard also has Meth
## still might need to add in an error for when isoreader goofs occasionally with the vendor data table when peak st and stop time are adjusted 

##################################################
## REASONS WHY YOU MAY RUN AN ERROR
# Is your AAstd name consistent with your file names?
# Are your labstd names consistent with your file names?
# Did you format the file name correctly? No extra "_", includes sample id, C or N, run with replicate number YYMMDD_HHMMSS_AA4_C_R1_xxxxxxxx OR YYMMDD_HHMMSS_Cal2003_C_R1_xxxxxxxx 
# Did you adjust the AAs in the standard run vector according to what your standards ran?
# Did you delete all of your junk peaks?
# Do you have any peaks in your sample that are not included in your AA standard runs? -- delete those 

##############################################################################
## ASUMPTIONS 
# This is applied after you do your peak corrections in isodat
# No need to remove extra columnsin the vendor table

# dxf file name example format:
## Standards:
# YYMMDD_HHMMSS_AA4_C_R1_xxxxxxxx
# YYMMDD_HHMMSS_AA4_C_R2_xxxxxxxx

## Samples:
# YYMMDD_HHMMSS_Cal2003_C_R1_xxxxxxxx
# YYMMDD_HHMMSS_Cal2003_C_R2_xxxxxxxx
# YYMMDD_HHMMSS_Cal2003_C_R3_xxxxxxxx
# YYMMDD_HHMMSS_Cal2005_C_R1_xxxxxxxx
# YYMMDD_HHMMSS_Cal2005_C_R2_xxxxxxxx
# YYMMDD_HHMMSS_Cal2005_C_R3_xxxxxxxx

# assumes the first five and last 3 peaks are always the one off runs and that there are no extra or "Junk" peaks





```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ProcessIsodataOuts)
```

```{r, echo=FALSE}

###########################################################
# # # # #####
# ## EXAMPLE
#### rm(list = ls(all.names = TRUE)) ## USE THIS TO CELAR ENVIRONMENT IF NESSARY 
# ## Where are your dxf files saved?
# file_data <- c("C:/Thermo/Isodat NT/Global/User/Conflo IV Interface/Conflo IV Interface/Results/2021 Copepods/N_AA6_cyn6_Fish1_ty0710_cal979905")
# ## AA std id name for that run
# AAStd_name <-  "AA6"
# ## AA that were measured in your standard during the run  ## AA_list <- c("Ala", "Gly", "Thr", "Ser", "Val", "Leu", "Ile", "NLeu", "Pro", "Asp", "Met", "Glu", "Phe", "Lys", "Arg")
# # Note - if you did not measure a value in your standard, you need to deleate that peak from your isodate files also for each sample 
# AA_list <- c(  "Val", "Leu", "Ile", "NLeu", "Pro", "Asp", "Met", "Glu", "Phe", "Lys", "Arg")
# ## Nitrogen or carbon
# C_N <- "N"
# ## Name of the folder your files are in (or some way to identfy this spicific run when saving the std data in other folders)
# fl_nm <- "N_AA6_cyn6_Fish1_ty0710_cal979905"
# 
# ## the oder AA are plotted in (type is like source, trophic, essentia/non. Run is the order that the machine measures them in  )
# order_AAs <- "Type" # "Type" "Run"
# 
# ## the sample name of your lab standard (McMahon lab has been using cyano and a fish so that is why the name is cyano and not labstd for now)
# cyano <- "Cyn6"
# fish_muscle <- "Fish1"
# 

# 
# file_data <- c("C:/Thermo/Isodat NT/Global/User/Conflo IV Interface/Conflo IV Interface/Results/2021 Copepods/N_AA7_cyn7_Fish2_ty969708_cal9608_TESTBUG")
file_data <- paste0(path.package(package = "ProcessIsodataOuts", quiet = FALSE),"/test_run")  
AAStd_name <-  "AA8"
# AA_list <- c("Ala", "Gly", "Thr", "Ser", "Val", "Leu", "Ile", "NLeu", "Pro", "Asp", "Met", "Glu", "Phe", "Lys", "Arg")
AA_list <- c( "Val", "Leu", "Ile", "NLeu", "Pro", "Asp", "Met", "Glu", "Phe", "Lys", "Arg")
C_N <- "N"
fl_nm <- "N_AA7_cyn7_Fish2_ty969708_cal9608_TESTBUG"
order_AAs <- "Type" # "type
cyano <- "Cyn8"
fish_muscle <- "Fish3"


# ## C_AA8_cyn8_f3_ty040616_cal040616
# file_data <- c("C:/Thermo/Isodat NT/Global/User/Conflo IV Interface/Conflo IV Interface/Results/2021 Copepods/C_AA8_cyn8_f3_ty040616_cal040616")
# AAStd_name <- "AA8"
# AA_list <- c("Ala", "Gly", "Thr", "Ser", "Val", "Leu", "Ile", "NLeu", "Pro", "Asp", "Met", "Glu", "Phe", "Lys", "Arg")
# C_N <- "C"
# fl_nm <- "C_AA8_cyn8_f3_ty040616_cal040616"
# order_AAs <- "Type" # "Type" "Run"
# cyano <- "cyn7"
# fish_muscle <- "fish2"



# # ## A separate place where you want your final sample data to be stored:
file_save <- "C:/Users/EcoGeoChemLab/Documents"
# 
# ## Where this file you are using now lives:
file_home <- "C:/Users/EcoGeoChemLab/isodat_processing"

## Carbon AA std files for your lab
file_save_AAstds_C <- "C:/Users/EcoGeoChemLab/Documents/AAStds_C"
## Carbon Labstd files for your lab
file_save_stds_C <- "C:/Users/EcoGeoChemLab/Documents/Stds_C"


## Nitrogen AA std files for your lab
file_save_AAstds_N <- "C:/Users/EcoGeoChemLab/Documents/AAStds_N"
## Nitrogen Labstd files for your lab
file_save_stds_N <- "C:/Users/EcoGeoChemLab/Documents/Stds_N"

##############################################################################
##############################################################################
## Code you shouldn't need to touch:

# file_sorc <- paste0(file_home, "/sorc") ## Where your source files are stored (These you should never have to touch, and should be the same if you are running normal data corrections or std test runs)

#######################
# source(paste0(file_sorc, "/process_CSIA_full_run.r"))     
outs <- process_CSIA_full_run()




```


```{r}

all_fn_std_df <- outs$all_fn_std_df
all_fn_df <- outs$all_fn_df
rm(outs)
```




